The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-05-06 RET_Hosts_CWR.tex
Updates from Overleaf

% Abstract of the paper
\begin{abstract}
Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a distinct class of astrophysical event. They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1. Their evolution on fast timescales has hindered high quality follow-up observations, such that their origin and explosion/emission mechanism remains unexplained. In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey. Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive host galaxy stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities for 44. We find that RETs explode exclusively in star-forming galaxies and are thus likely associated with massive stars. Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs, indicating a link to young stellar populations, similar to stripped-envelope SNe. RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies. There are no clear relationships between properties of the host galaxies and the peak magnitudes or decline rates of the transients themselves.

@@

 Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973}, were only unequivocally linked to collapsing massive stars through their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}. Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[e.g.][]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}. The second exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g. \citealt{Quimby2011, Gal-Yam2012}). Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than regular CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citep{Li2011}. The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly formed, rapidly rotating magnetar.

@@

In this paper, we present the first comprehensive study of the host galaxies of RETs. We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} using the final year of data as well as more refined discovery techniques. Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients. For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1.

@@

Of objects passing these cuts, the RETs cluster at shorter timescales and bluer colours than other SNe, even in the observer frame. However, using photometric data points directly has several problems that can be improved. For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights, thus making it impossible to measure the peak colour in a number of cases. Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range. To negate this issue, we use lightcurves interpolated using Gaussian Processes (GP) as presented in \citetalias{Pursiainen2018}. The interpolated light curves have a 0.5 day cadence and every epoch and band has a flux value, and an associated uncertainty. Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$ vs. $t_{\mathrm{rise; r}}$ parameter space (Fig. \ref{fig:selection}), where $t_{\mathrm{rise; r}}$ is the time to rise from non-detection to peak $r$-band brightness, and the $g-r$ colour is measured at peak brightness. We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness). The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, and the parameter space can be seen in Fig. \ref{fig:selection}.

@@

The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium. Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation. Using the Baldwin-Phillips-Terlevich diagram (Fig. \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN. We note than only 11 of the 44 RET host spectra have the necessary lines to plot a BPT diagram. This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence of AGN amongst the 11 hosts in those diagrams either.

@@

\subsection{Correlations between lightcurve and host galaxy properties \label{subsec:disc_correlations}}
Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies. For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFRs \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}. In Fig. \ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and decline rate parameterised as $t_{\mathrm{half}}$, the time taken for the LC to decline to half the peak brightness (lower panels) and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels). The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a simple blackbody SED. There is no correlation between decline rate and either stellar mass or sSFR, while there are hints of a trend between peak magnitude and both mass and sSFR. These apparent trends are driven by the more extreme hosts (the three with $\log\left(M_*/M_{\odot}\right) < 9$ and one with very high mass/low sSFR). Assuming that these points are not outliers, the trends are still likely driven by selection effects. At higher redshifts, only the brighter transients are recovered by the survey and our selection method, while at those redshifts only the more massive galaxies are detected. This effect can be seen in panel a) of Fig. \ref{fig:ret_v_host}, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in panel b. It is hoped that a complete, volume-limited sample of RETs will be obtained by The Rubin Observatory Legacy Survey of Space and Time (LSST) allowing the removal of these biases in order to reveal any underlying relationships.

@@

DES13X3gms &  $43.3 \pm 27.7$ &   $10.9 \pm 7.9$ &    $32.9 \pm 7.9$ &               - &               - &               - &               - &   $2.0 \pm 7.6$ &   $17.0 \pm 7.1$ &    $6.3 \pm 9.5$ &                - \\
DES13C1tgd &    $1.9 \pm 0.7$ &    $0.0 \pm 0.1$ &     $0.0 \pm 0.1$ &   $0.5 \pm 0.1$ &   $1.6 \pm 0.1$ &   $1.1 \pm 0.0$ &   $0.8 \pm 0.0$ &   $0.9 \pm 0.2$ &    $1.3 \pm 0.1$ &    $0.2 \pm 0.1$ &    $4.5 \pm 0.2$ \\
DES13S2wxf &   $22.1 \pm 5.3$ &    $3.2 \pm 2.0$ &     $9.8 \pm 2.0$ &               - &               - &               - &               - &   $2.4 \pm 1.0$ &    $4.3 \pm 0.8$ &    $4.5 \pm 2.1$ &                - \\
DES13X1hav &  $31.4 \pm 49.1$ &  $10.5 \pm 12.0$ &   $31.9 \pm 12.0$ &               - &               - &               - &               - &   $0.0 \pm 6.2$ &   $5.2 \pm 11.5$ &   $10.6 \pm 4.8$ &                - \\
DES13X3nyg &   $15.1 \pm 1.6$ &    $3.2 \pm 0.4$ &     $9.8 \pm 0.4$ &               - &               - &               - &               - &   $0.5 \pm 0.4$ &    $0.0 \pm 0.6$ &    $3.3 \pm 0.4$ &                - \\
DES13X3gmd &   $18.8 \pm 5.3$ &                - &                 - &               - &               - &               - &               - &   $1.9 \pm 3.8$ &    $2.3 \pm 2.7$ &    $7.0 \pm 8.3$ &                - \\
DES13X2wvv &  $61.5 \pm 14.4$ &    $7.4 \pm 3.6$ &    $22.6 \pm 3.6$ &               - &               - &               - &               - &   $2.7 \pm 4.9$ &    $1.1 \pm 3.3$ &   $10.3 \pm 2.8$ &                - \\
DES14S2anq &  $486.0 \pm 0.4$ &   $74.9 \pm 1.1$ &   $227.1 \pm 1.1$ &  $10.3 \pm 5.1$ &  $31.1 \pm 5.1$ &  $43.1 \pm 4.0$ &  $31.1 \pm 4.5$ &  $31.5 \pm 1.4$ &   $58.9 \pm 1.4$ &  $114.0 \pm 1.4$ &  $240.0 \pm 0.9$ \\
DES14X1bnh &   $23.1 \pm 1.2$ &                - &                 - &               - &               - &               - &               - &   $0.4 \pm 0.4$ &    $3.1 \pm 0.5$ &                - &                - \\
DES15S1fli &   $33.3 \pm 3.3$ &    $3.4 \pm 1.5$ &    $10.5 \pm 1.5$ &               - &               - &               - &               - &   $3.0 \pm 1.5$ &    $4.2 \pm 0.8$ &    $8.7 \pm 0.4$ &                - \\
DES15S1fll &  $75.2 \pm 78.8$ &  $13.6 \pm 10.8$ &   $41.3 \pm 10.8$ &   $1.4 \pm 3.9$ &   $4.4 \pm 3.9$ &   $2.7 \pm 2.6$ &   $4.9 \pm 2.8$ &  $0.6 \pm 19.2$ &  $14.3 \pm 16.6$ &  $13.4 \pm 10.2$ &   $40.9 \pm 5.2$ \\
DES14X3pkl &   $13.5 \pm 9.5$ &    $2.6 \pm 0.8$ &     $7.9 \pm 0.8$ &   $0.7 \pm 0.4$ &   $2.2 \pm 0.4$ &   $3.5 \pm 0.5$ &   $1.9 \pm 0.3$ &   $1.7 \pm 2.7$ &    $2.6 \pm 2.8$ &    $0.0 \pm 2.1$ &   $10.4 \pm 0.7$ \\
DES13X3npb &   $14.6 \pm 4.1$ &    $1.4 \pm 0.2$ &     $4.2 \pm 0.2$ &               - &               - &               - &               - &   $2.3 \pm 0.2$ &    $4.0 \pm 0.2$ &    $5.7 \pm 0.2$ &                - \\
DES15X2ead &   $9.7 \pm 10.0$ &    $0.8 \pm 0.8$ &     $2.3 \pm 0.8$ &   $0.8 \pm 0.4$ &   $2.5 \pm 0.4$ &   $3.5 \pm 0.3$ &   $2.2 \pm 0.6$ &   $2.9 \pm 2.5$ &    $1.3 \pm 1.7$ &    $2.3 \pm 0.8$ &   $11.5 \pm 0.3$ \\
DES14S2plb &   $14.1 \pm 0.7$ &    $1.0 \pm 0.1$ &     $3.0 \pm 0.1$ &   $1.2 \pm 0.0$ &   $3.6 \pm 0.0$ &   $2.3 \pm 0.0$ &   $1.8 \pm 0.0$ &   $2.0 \pm 0.1$ &    $2.3 \pm 0.1$ &    $4.8 \pm 0.1$ &   $12.2 \pm 0.0$ \\
DES14S2pli &   $13.7 \pm 0.9$ &    $0.6 \pm 0.1$ &     $1.7 \pm 0.1$ &               - &               - &               - &               - &   $0.0 \pm 0.4$ &    $1.6 \pm 0.3$ &    $3.5 \pm 0.1$ &                - \\
DES14C3tnz &   $23.1 \pm 4.5$ &    $3.0 \pm 1.0$ &     $9.2 \pm 1.0$ &               - &               - &               - &               - &   $1.1 \pm 0.9$ &    $4.5 \pm 1.5$ &    $4.4 \pm 3.8$ &                - \\
DES15X3mxf &   $29.5 \pm 3.4$ &    $1.7 \pm 0.5$ &     $5.2 \pm 0.5$ &               - &               - &               - &               - &   $1.1 \pm 2.8$ &    $4.0 \pm 1.2$ &    $5.0 \pm 0.5$ &                - \\
DES15C3lpq &   $37.0 \pm 9.8$ &    $8.6 \pm 3.3$ &    $26.2 \pm 3.3$ &               - &               - &               - &               - &   $4.2 \pm 2.6$ &    $2.3 \pm 2.6$ &    $9.1 \pm 4.5$ &                - \\
DES15C3nat &   $21.6 \pm 1.5$ &                - &                 - &               - &               - &               - &               - &   $1.5 \pm 0.6$ &    $4.2 \pm 1.4$ &                - &                - \\
DES15C3mgq &  $17.0 \pm 20.8$ &    $6.3 \pm 2.4$ &    $19.1 \pm 2.4$ &   $0.4 \pm 1.3$ &   $1.3 \pm 1.3$ &   $1.2 \pm 0.7$ &   $0.0 \pm 3.6$ &   $1.8 \pm 5.1$ &    $1.7 \pm 4.0$ &    $6.2 \pm 2.9$ &   $10.6 \pm 0.8$ \\
DES15E2nqh &  $34.7 \pm 22.4$ &    $9.3 \pm 3.6$ &    $28.2 \pm 3.6$ &               - &               - &               - &               - &   $2.4 \pm 4.3$ &    $4.8 \pm 5.2$ &    $7.7 \pm 5.1$ &                - \\
DES15C3opk &   $10.5 \pm 6.5$ &    $5.0 \pm 3.1$ &    $15.1 \pm 3.1$ &               - &               - &               - &               - &   $0.7 \pm 1.2$ &    $1.8 \pm 0.9$ &    $2.9 \pm 3.7$ &                - \\
DES15C3opp &   $15.5 \pm 3.3$ &    $1.7 \pm 0.6$ &     $5.2 \pm 0.6$ &               - &               - &               - &               - &   $0.7 \pm 2.1$ &    $2.9 \pm 1.5$ &    $3.1 \pm 0.7$ &                - \\
DES16E2pv  &  $39.7 \pm 12.2$ &    $6.0 \pm 9.5$ &    $18.0 \pm 9.5$ &               - &               - &               - &               - &   $0.3 \pm 4.9$ &    $5.9 \pm 5.1$ &    $6.9 \pm 4.9$ &                - \\
DES16S1bbp &  $37.2 \pm 13.0$ &    $7.5 \pm 1.7$ &    $22.9 \pm 1.7$ &   $0.7 \pm 0.4$ &   $2.1 \pm 0.4$ &   $2.8 \pm 1.3$ &   $2.0 \pm 0.4$ &   $2.9 \pm 2.7$ &    $6.0 \pm 1.9$ &   $12.2 \pm 2.3$ &   $24.2 \pm 0.8$ \\
DES16X3cxn &   $23.5 \pm 5.6$ &    $1.6 \pm 2.6$ &     $4.9 \pm 2.6$ &               - &               - &               - &               - &   $0.0 \pm 2.2$ &    $0.7 \pm 1.4$ &    $4.0 \pm 1.0$ &                - \\
DES16C1cbd &    $9.3 \pm 1.8$ &    $0.6 \pm 0.3$ &     $1.8 \pm 0.3$ &               - &               - &               - &               - &   $0.8 \pm 0.1$ &    $1.0 \pm 0.1$ &    $1.9 \pm 0.1$ &                - \\
DES16X3ega &   $28.2 \pm 2.1$ &    $0.9 \pm 1.0$ &     $2.8 \pm 1.0$ &   $1.0 \pm 0.8$ &   $3.0 \pm 0.8$ &   $2.8 \pm 0.4$ &   $1.5 \pm 0.9$ &   $2.0 \pm 0.8$ &    $4.4 \pm 0.7$ &    $5.8 \pm 0.5$ &   $14.5 \pm 0.4$ \\
DES16X3erw &   $31.6 \pm 4.0$ &    $2.9 \pm 1.6$ &     $8.8 \pm 1.6$ &               - &               - &               - &               - &   $3.4 \pm 1.7$ &    $2.1 \pm 1.5$ &    $7.2 \pm 0.7$ &                - \\
DES16C3gin &   $17.1 \pm 2.8$ &    $1.5 \pm 0.4$ &     $4.4 \pm 0.4$ &               - &               - &               - &               - &   $1.6 \pm 1.1$ &    $0.0 \pm 1.2$ &    $4.3 \pm 0.6$ &   $10.1 \pm 0.5$ \\
DES16S1dxu &  $96.3 \pm 33.0$ &   $16.4 \pm 8.4$ &    $49.5 \pm 8.4$ &   $0.8 \pm 2.5$ &   $2.4 \pm 2.5$ &   $1.2 \pm 3.6$ &   $3.7 \pm 1.8$ &   $5.5 \pm 6.9$ &    $9.1 \pm 4.8$ &   $22.8 \pm 3.9$ &   $39.2 \pm 1.2$ \\
DES16X1eho &    $6.6 \pm 0.9$ &                - &                 - &               - &               - &               - &               - &   $0.0 \pm 0.3$ &    $1.2 \pm 0.6$ &    $1.4 \pm 0.8$ &                - \\
DES17C3gop &  $21.1 \pm 17.3$ &    $2.5 \pm 2.4$ &     $7.6 \pm 2.4$ &               - &               - &               - &               - &   $2.7 \pm 2.4$ &    $5.3 \pm 3.2$ &    $4.8 \pm 1.4$ &                - \\

>>>>

% Abstract of the paper
\begin{abstract}
Rapidly evolving transients (RETs), also termed fast blue optical transients (FBOTs), are a distinct class of astrophysical event. They are characterised by lightcurves that decline much faster than standard supernovae (SNe), span vast ranges in peak luminosity and can be seen to redshifts greater than 1. Their evolution on fast timescales has hindered high quality follow-up observations, such that their origin and explosion/emission mechanism remains unexplained. In this paper we define the largest sample of RETs to date, comprising 106 objects from the Dark Energy Survey, and perform the first substantial analysis of RET host galaxies. Using deep-stacked photometry and emission-lines from OzDES spectroscopy, we derive stellar masses and star-formation rates (SFRs) for 49 host galaxies, and metallicities for 37. We find that RETs explode exclusively in star-forming galaxies and are thus likely associated with massive stars. Comparing RET hosts to samples of host galaxies of other explosive transients as well as field galaxies, we find that RETs prefer galaxies with high specific SFRs, indicating a link to young stellar populations, similar to stripped-envelope SNe. RET hosts appear to show a lack of chemical enrichment, their metallicities akin to long duration gamma-ray bursts and superluminous SN host galaxies. There are no clear relationships between properties of the host galaxies and the peak magnitudes or decline rates of the transients themselves.

@@

 Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973}, were only unequivocally linked to collapsing massive stars through their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}. Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[e.g.][]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SNe Ic, which themselves make up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}. The second exotic class of SNe is the particularly bright superluminous supernovae (SLSNe; e.g. \citealt{Quimby2011, Gal-Yam2012}). Originally grouped due to their slowly-evolving lightcurves and extreme luminosity (peaking at $M_B < -21$~mag; 10-100 times brighter than regular CCSNe), recent observations have revealed a continuum of spectroscopically similar objects with peaks as faint as $M_B \sim -19$~mag \citep{DeCia2018,Lunnan2018,Angus2019}, similar to the bright end of the CCSN luminosity function \citep{Li2011}. The lightcurve evolution of SLSNe is not well described by models of Ni-56 decay, with the most popular alternative hypothesis being the magnetic coupling of the ejecta with the spin down of a newly formed, rapidly rotating magnetar.

@@

In this paper, we present the first comprehensive study of the host galaxies of RETs. We make use of the final DES sample, which builds on \citetalias{Pursiainen2018} by adding the 5th and final year of DES-SN observations as well as more refined discovery techniques. Using the deep DES photometry from \citet[hereafter W20]{Wiseman2020} and spectra from OzDES \citep{Lidman2020} we derive host galaxy properties in order to compare them to samples of CCSNe, LGRBs, and SLSNe, as well as the individual local rapid transients. For clarity, we will use the term RET to refer only to events in the high-redshift samples of DES and PS1.

@@

Of objects passing these cuts, the RETs cluster at shorter timescales and bluer colours than other SNe, even in the observer frame. However, using photometric data points directly has several problems that can be improved. For one, measuring peak colour is problematic: DES-SN did not always observe $g$- and $r$-bands on the same or even consecutive nights, thus making it impossible to measure the peak colour in a number of cases. Measuring rise times of 10-15 days is difficult to perform with a one week cadence when it has to be done without fitting a light curve model, hence the rise time values are spread over a wide range. To negate this issue, we use lightcurves interpolated using Gaussian Processes (GP) as presented in \citetalias{Pursiainen2020}. The interpolated light curves have a 0.5 day cadence and every epoch and band has a flux value, and an associated uncertainty. Using this technique, SNe Ia and RETs populate two distinct regions of $g-r$ vs. $t_{\mathrm{rise; r}}$ parameter space (Fig. \ref{fig:selection}), where $t_{\mathrm{rise; r}}$ is the time to rise from non-detection to peak $r$-band brightness, and the $g-r$ colour is measured at peak brightness. We define a region in this parameter space which minimises the contamination of non-RETs (purity) while maximising the total fraction of RETs (completeness). The resulting limits are $-1.5 < g-r < 0.6 $ and $t_{\mathrm{rise; r}} <16.5$, and the parameter space can be seen in Fig. \ref{fig:selection}.

@@

The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium. Emission lines originate from regions of ionised gas, but there are a number of possible causes of this ionisation. Using the Baldwin-Phillips-Terlevich diagram (Fig. \ref{fig:bpt}; \citealt{Baldwin1981}), we demonstrate that the emission line ratios measured in RET hosts are consistent with ionisation caused by star-formation as opposed to AGN. We note than only 12 of the 45 RET host spectra have the necessary lines to plot a BPT diagram. This is also the case for the \SII~and \OI~versions of the diagram, and we find no evidence of AGN amongst the 11 hosts in those diagrams either.

@@

\subsection{Correlations between lightcurve and host galaxy properties \label{subsec:disc_correlations}}
Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies. For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFRs \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}. In Fig. \ref{fig:ret_v_host} we show the RET peak magnitude (upper panels) and lightcurve width parameterised as $t_{\mathrm{half}}$, the time the lightcurve is above half the peak brightness (lower panels), and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels). The decline rates have been converted to the rest-frame of the transients, while the peak magnitudes have been k-corrected assuming a simple blackbody SED. There is no correlation between decline rate and either stellar mass or sSFR, while there are hints of a trend between peak magnitude and both mass and sSFR. These apparent trends are driven by the more extreme hosts (the three with $\log\left(M_*/M_{\odot}\right) < 9$ and one with very high mass/low sSFR). Assuming that these points are not outliers, the trends are still likely driven by selection effects. At higher redshifts, only the brighter transients are recovered by the survey and our selection method, while at those redshifts only the more massive galaxies are detected. This effect can be seen in panel a) of Fig. \ref{fig:ret_v_host}, with redshift increasing from the lower left to the upper right, while the same is true from the upper left to lower right in panel b. It is hoped that a complete, volume-limited sample of RETs will be obtained by The Rubin Observatory Legacy Survey of Space and Time (LSST) allowing the removal of these biases in order to reveal any underlying relationships.

@@

DES13X3gms  &   $1.2 \pm 14.8$ &  $0.3 \pm 1.8$ &   $0.9 \pm 1.8$ &              - &               - &              - &              - &  $0.0 \pm 1.9$ &  $15.1 \pm 2.0$ &   $0.7 \pm 1.5$ &               - \\
DES13C1tgd  &    $1.6 \pm 1.5$ &  $0.0 \pm 0.5$ &   $0.0 \pm 0.5$ &  $0.7 \pm 0.6$ &   $2.2 \pm 0.6$ &  $1.5 \pm 0.3$ &  $1.0 \pm 0.4$ &  $0.4 \pm 0.5$ &   $1.1 \pm 0.5$ &   $0.3 \pm 0.5$ &   $5.8 \pm 0.8$ \\
DES13S2wxf  &  $32.7 \pm 10.5$ &  $1.3 \pm 1.1$ &   $4.1 \pm 1.1$ &              - &               - &              - &              - &  $1.9 \pm 1.2$ &   $2.1 \pm 1.0$ &   $1.8 \pm 1.1$ &               - \\
DES13X1hav  &    $3.0 \pm 1.2$ &  $1.0 \pm 0.6$ &   $3.0 \pm 0.6$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.5 \pm 0.5$ &   $0.9 \pm 0.3$ &               - \\
DES13X3nyg  &    $2.6 \pm 0.6$ &  $0.1 \pm 0.4$ &   $0.3 \pm 0.4$ &              - &               - &              - &              - &  $0.1 \pm 0.2$ &   $0.0 \pm 0.2$ &   $0.1 \pm 0.1$ &               - \\
DES13X3gmd  &    $2.7 \pm 0.7$ &              - &               - &              - &               - &              - &              - &  $0.1 \pm 0.4$ &   $0.3 \pm 0.4$ &   $1.3 \pm 1.0$ &               - \\
DES13C3bcok &    $3.6 \pm 3.8$ &  $0.7 \pm 1.2$ &   $2.2 \pm 1.2$ &              - &               - &              - &              - &  $0.0 \pm 1.2$ &   $2.0 \pm 1.4$ &   $2.3 \pm 1.0$ &  $10.8 \pm 3.0$ \\
DES13X2wvv  &   $16.4 \pm 2.7$ &  $2.9 \pm 1.4$ &   $8.8 \pm 1.4$ &              - &               - &              - &              - &  $1.1 \pm 1.3$ &   $0.6 \pm 1.2$ &   $4.3 \pm 1.1$ &               - \\
DES14X1bnh  &    $8.3 \pm 0.8$ &              - &               - &              - &               - &              - &              - &  $0.1 \pm 0.3$ &   $1.0 \pm 0.3$ &               - &               - \\
DES15S1fli  &   $15.0 \pm 1.6$ &  $1.3 \pm 1.0$ &   $3.9 \pm 1.0$ &              - &               - &              - &              - &  $1.4 \pm 0.8$ &   $2.2 \pm 0.6$ &   $4.3 \pm 0.5$ &               - \\
DES15S1fll  &   $10.3 \pm 2.5$ &  $5.0 \pm 2.0$ &  $15.2 \pm 2.0$ &  $0.5 \pm 1.1$ &   $1.4 \pm 1.1$ &  $0.8 \pm 0.8$ &  $1.5 \pm 0.8$ &  $0.6 \pm 1.1$ &   $2.5 \pm 1.3$ &   $4.2 \pm 1.5$ &  $15.4 \pm 1.4$ \\
DES14X3pkl  &    $2.5 \pm 1.2$ &  $0.8 \pm 0.4$ &   $2.3 \pm 0.4$ &  $0.2 \pm 0.2$ &   $0.5 \pm 0.2$ &  $0.8 \pm 0.2$ &  $0.4 \pm 0.2$ &  $0.4 \pm 0.5$ &   $0.6 \pm 0.6$ &   $0.0 \pm 0.7$ &   $2.3 \pm 0.3$ \\
DES13X3npb  &   $15.9 \pm 6.6$ &  $0.8 \pm 0.8$ &   $2.4 \pm 0.8$ &              - &               - &              - &              - &  $2.0 \pm 0.7$ &   $2.6 \pm 0.4$ &   $3.3 \pm 0.8$ &               - \\
DES15X2ead  &  $31.4 \pm 23.5$ &  $1.6 \pm 3.0$ &   $4.8 \pm 3.0$ &  $1.1 \pm 1.6$ &   $3.5 \pm 1.6$ &  $5.3 \pm 1.7$ &  $3.2 \pm 1.9$ &  $9.6 \pm 7.9$ &   $4.5 \pm 6.0$ &   $5.4 \pm 3.1$ &  $16.7 \pm 1.9$ \\
DES14S2plb  &   $54.5 \pm 7.2$ &  $4.5 \pm 2.1$ &  $13.5 \pm 2.1$ &  $5.6 \pm 1.8$ &  $16.9 \pm 1.8$ &  $9.5 \pm 0.9$ &  $7.1 \pm 0.7$ &  $6.5 \pm 2.0$ &   $7.9 \pm 1.7$ &  $19.3 \pm 1.5$ &  $53.4 \pm 1.7$ \\
DES14S2pli  &    $7.7 \pm 1.1$ &  $0.4 \pm 0.4$ &   $1.2 \pm 0.4$ &              - &               - &              - &              - &  $0.0 \pm 0.6$ &   $1.1 \pm 0.5$ &   $2.4 \pm 0.3$ &               - \\
DES14C3tnz  &    $4.2 \pm 0.9$ &  $0.4 \pm 0.3$ &   $1.3 \pm 0.3$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.4 \pm 0.3$ &   $0.4 \pm 0.5$ &               - \\
DES15X3mxf  &    $4.8 \pm 0.7$ &  $0.4 \pm 0.3$ &   $1.2 \pm 0.3$ &              - &               - &              - &              - &  $0.6 \pm 0.5$ &   $0.7 \pm 0.4$ &   $1.1 \pm 0.3$ &               - \\
DES15C3lpq  &    $3.9 \pm 0.8$ &  $0.5 \pm 0.3$ &   $1.6 \pm 0.3$ &              - &               - &              - &              - &  $0.5 \pm 0.3$ &   $0.2 \pm 0.2$ &   $0.6 \pm 0.2$ &               - \\
DES15C3nat  &    $3.9 \pm 0.6$ &              - &               - &              - &               - &              - &              - &  $0.2 \pm 0.1$ &   $0.2 \pm 0.1$ &               - &               - \\
DES15C3mgq  &    $4.1 \pm 2.5$ &  $1.1 \pm 0.5$ &   $3.2 \pm 0.5$ &  $0.1 \pm 0.2$ &   $0.2 \pm 0.2$ &  $0.2 \pm 0.2$ &  $0.0 \pm 0.4$ &  $0.6 \pm 0.8$ &   $0.4 \pm 0.7$ &   $1.2 \pm 0.5$ &   $1.4 \pm 0.2$ \\
DES15E2nqh  &    $0.7 \pm 1.0$ &  $0.9 \pm 0.5$ &   $2.8 \pm 0.5$ &              - &               - &              - &              - &  $0.4 \pm 0.4$ &   $0.9 \pm 0.5$ &   $0.8 \pm 0.5$ &               - \\
DES15C3opk  &    $1.6 \pm 0.8$ &  $0.5 \pm 0.3$ &   $1.4 \pm 0.3$ &              - &               - &              - &              - &  $0.1 \pm 0.3$ &   $0.3 \pm 0.2$ &   $0.4 \pm 0.3$ &               - \\
DES15C3opp  &    $2.5 \pm 0.7$ &  $0.2 \pm 0.2$ &   $0.5 \pm 0.2$ &              - &               - &              - &              - &  $0.2 \pm 0.4$ &   $0.5 \pm 0.3$ &   $0.4 \pm 0.1$ &               - \\
DES16E2pv   &    $2.5 \pm 0.6$ &  $0.7 \pm 1.0$ &   $2.2 \pm 1.0$ &              - &               - &              - &              - &  $0.0 \pm 0.4$ &   $0.7 \pm 0.5$ &   $1.3 \pm 0.6$ &               - \\
DES16S1bbp  &   $21.9 \pm 3.5$ &  $3.8 \pm 0.9$ &  $11.4 \pm 0.9$ &  $0.3 \pm 0.4$ &   $1.0 \pm 0.4$ &  $1.5 \pm 0.7$ &  $0.9 \pm 0.3$ &  $1.4 \pm 1.1$ &   $3.4 \pm 0.9$ &   $6.4 \pm 1.0$ &  $11.1 \pm 0.6$ \\
DES16X3cxn  &    $2.3 \pm 0.5$ &  $0.3 \pm 0.4$ &   $0.9 \pm 0.4$ &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.2 \pm 0.2$ &   $0.6 \pm 0.2$ &               - \\
DES16C1cbd  &    $4.4 \pm 1.8$ &  $0.4 \pm 0.8$ &   $1.2 \pm 0.8$ &              - &               - &              - &              - &  $0.4 \pm 0.4$ &   $0.4 \pm 0.4$ &   $1.1 \pm 0.4$ &               - \\
DES16C3axz  &   $26.8 \pm 2.6$ &  $2.3 \pm 0.8$ &   $7.0 \pm 0.8$ &  $2.6 \pm 0.6$ &   $7.7 \pm 0.6$ &  $5.4 \pm 0.5$ &  $4.0 \pm 0.5$ &  $2.7 \pm 0.9$ &   $5.6 \pm 0.8$ &   $9.9 \pm 0.8$ &  $29.1 \pm 0.7$ \\
DES16X3erw  &    $5.9 \pm 0.9$ &  $0.8 \pm 0.6$ &   $2.6 \pm 0.6$ &              - &               - &              - &              - &  $0.6 \pm 0.4$ &   $0.4 \pm 0.4$ &   $1.9 \pm 0.3$ &               - \\
DES16C3gin  &    $5.8 \pm 1.2$ &  $0.5 \pm 0.4$ &   $1.6 \pm 0.4$ &              - &               - &              - &              - &  $0.5 \pm 0.6$ &   $0.0 \pm 0.6$ &   $1.6 \pm 0.4$ &   $2.5 \pm 0.4$ \\
DES16S1dxu  &   $29.2 \pm 3.6$ &  $6.4 \pm 1.9$ &  $19.5 \pm 1.9$ &  $0.4 \pm 1.0$ &   $1.2 \pm 1.0$ &  $0.5 \pm 1.0$ &  $1.4 \pm 0.7$ &  $1.7 \pm 1.1$ &   $2.9 \pm 0.9$ &   $8.6 \pm 1.1$ &  $16.5 \pm 0.8$ \\
DES16X1eho  &    $2.5 \pm 0.9$ &              - &               - &              - &               - &              - &              - &  $0.0 \pm 0.3$ &   $0.2 \pm 0.4$ &   $0.7 \pm 0.5$ &               - \\
DES17C3gop  &    $2.0 \pm 0.8$ &  $0.2 \pm 0.3$ &   $0.6 \pm 0.3$ &              - &               - &              - &              - &  $0.2 \pm 0.3$ &   $0.6 \pm 0.4$ &   $0.5 \pm 0.2$ &               - \\
